Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-02 paper/ms.tex
update paper

\begin{figure*}[!ht]
	\gridline{\fig{mwscmatchstats.png}{0.95\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{dias14matchstats.png}{0.95\textwidth}{}}
	\caption{
    {\it Top.} Cross-match statistics from
    \cite{Kharchenko_et_al_2013} cluster members to Gaia-DR2. A
    histogram of the distances between matched stars is on the left; a
    histogram of the difference between the true $G$-band magnitude
    and that predicted from 2MASS photometry in the middle; a scatter
    plot of the same magnitude difference as a function of $G$-band
    magnitude is on the right.
    {\it Bottom.} Same, but cross-matching \cite{dias_proper_2014}
    cluster members to Gaia-DR2.
	}
	\label{fig:xmatch_info}
\end{figure*}

@@

\begin{figure}[!t]
	\gridline{\fig{astromresidual_hist.png}{0.5\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{astromresidual_quiver.png}{0.5\textwidth}{}}
  %\vspace{-0.8cm}
	%\gridline{\fig{astromresidual_apertures.png}{0.5\textwidth}{}}
	\vspace{-0.8cm}
    \caption{
		{\it Top.} {\bf Histogram of astrometric residual.} The $x$-axis shows 
		the distance between the measured centroid positions of stars, 
		compared to the predicted positions from the WCS solution.
		{\it Bottom.} {\bf Vector plot of astrometric residual.} Each arrow is 
		the vector from the measured to the projected star position. 
		Directions are correct, but lengths are 50 times their true size for 
		visualization purposes.
        The systematic error in the top-right corner is a typical problem in 
        wide-field astrometry.
        The frame chosen for this plot is the photometric reference frame used 
        for Sector 6, Camera 1, CCD 1; we automatically 
        impose cutoffs on the median and $90^{\rm th}$ percentile of the 
        astrometric residual in order to ensure similar levels of astrometric 
        precision are maintained throughout the reduction.
	}
	\label{fig:astromresid}
\end{figure}

@@

\begin{figure*}[t]
    \begin{center}
		\includegraphics[height=0.9\textheight]{mag_vs_epdparams.png}
    \end{center}
    \vspace{-0.5cm}
    \caption{
      {\bf Flux as a function of ``external parameters'' for four
      representative stars.} The left two columns are stars at the
      corner of a camera's field; the right two columns are from the
      centers.
      Each row shows a different parameter along the $x$-axis, given
      in text at the bottom right of each subplot.
      ``Hooks'' are common features in flux as a function of
      temperature and centroid position.
      \S~\ref{sec:flux_vs_external_parameters} gives a verbose
      description.
     \label{fig:flux_vs_external_parameters}
    }
\end{figure*}

@@

\item {\it Flux vs.\ centroid positions}. The flux as a function of
  centroid position often showed non-linear ``hooks'' (see Figure
    \ref{fig:flux_vs_external_parameters}). Most of the data points from a 
    given orbit reside at a given
    level, but about 10\% are in a tail. This was seen in light curves
    all across the TESS field of view.

@@

\begin{figure*}[!t]
	%\gridline{
	%  \fig{cluster_field_star_positions.png}{0.49\textwidth}{}
	%  \fig{sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png}{0.49\textwidth}{}
	%}
	\begin{center}
		\leavevmode
		\includegraphics[width=0.97\textwidth]{galacticcoords_cluster_field_star_positions.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Positions of light curves from Sectors 6
			and 7 in galactic coordinates.}
		    Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm Rp}<16$ target stars.
		\label{fig:lcgalactic}
	}
\end{figure*}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{quilt_PCs.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf Six of the \numberpcs candidate transiting planets identified
    from this work.}
    Black points are detrended flux measurements, phased to the
    best-fit orbital period, indicated in the lower right of each panel.
    Best-fit models are fit as described in \S~\ref{subsec:ctois}, and
    shown with blue lines.
    For display purpses, a window of $\pm 4$ transit durations from the
    mid-point is displayed.
    The vetting reports for these objects are available at XXX.	%FIXME
    % TODO: include age? T mag?
    The Gaia source identifiers are
    a): 5605128927705695232, 
    b): 3125263468681400320, 
    c): 5510676828723793920, 
    d): 3007171311355035136, 
    e): 5617126180115568256, 
    f): 3220266049321724416.   
	\label{fig:ctoi_quilt}
	}
\end{figure*}

>>>>

\begin{figure*}[!ht]
	\gridline{\fig{mwscmatchstats.png}{0.95\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{dias14matchstats.png}{0.95\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
    {\it Top.} Cross-match statistics from
    \cite{Kharchenko_et_al_2013} cluster members to Gaia-DR2. A
    histogram of the distances between matched stars is on the left; a
    histogram of the difference between the true $G$-band magnitude
    and that predicted from 2MASS photometry is in the middle; a scatter
    plot of the same magnitude difference as a function of $G$-band
    magnitude is on the right.
    {\it Bottom.} Same, but cross-matching \cite{dias_proper_2014}
    cluster members to Gaia-DR2.
	}
	\label{fig:xmatch_info}
\end{figure*}

@@

\begin{figure}[!t]
	\gridline{\fig{astromresidual_hist.png}{0.5\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{astromresidual_quiver.png}{0.5\textwidth}{}}
  %\vspace{-0.8cm}
	%\gridline{\fig{astromresidual_apertures.png}{0.5\textwidth}{}}
	\vspace{-0.8cm}
    \caption{
		{\it Top.} {\bf Histogram of astrometric residual.} The $x$-axis shows 
		the distance between the measured centroid positions of stars, 
		compared to the predicted positions from the WCS solution.
		{\it Bottom.} {\bf Vector plot of astrometric residual.} Each arrow is 
		the vector from the measured to the projected star position. 
		Directions are correct, but lengths are 50 times their true size for 
		visualization purposes.
    The systematic error in the top-right corner is a typical
    problem generic to wide-field astrometry.
    The frame chosen for this plot is the photometric reference frame used 
    for Sector 6, Camera 1, CCD 1; we automatically 
    impose cutoffs on the median and $90^{\rm th}$ percentile of the 
    astrometric residual in order to ensure similar levels of astrometric 
    precision are maintained throughout the reduction.
	}
	\label{fig:astromresid}
\end{figure}

@@

% \begin{figure*}[t]
%     \begin{center}
% 		\includegraphics[height=0.9\textheight]{mag_vs_epdparams.png}
%     \end{center}
%     \vspace{-0.5cm}
%     \caption{
%       {\bf Flux as a function of ``external parameters'' for four
%       representative stars.} The left two columns are stars at the
%       corner of a camera's field; the right two columns are from the
%       centers.
%       Each row shows a different parameter along the $x$-axis, given
%       in text at the bottom right of each subplot.
%       ``Hooks'' are common features in flux as a function of
%       temperature and centroid position.
%       \S~\ref{sec:flux_vs_external_parameters} gives a verbose
%       description.
%      \label{fig:flux_vs_external_parameters}
%     }
% \end{figure*}

@@

\item {\it Flux vs.\ centroid positions}. The flux as a function of
  centroid position often showed non-linear ``hooks''
    %(see Figure \ref{fig:flux_vs_external_parameters}).
    Most of the data points from a given orbit reside at a given
    level, but about 10\% are in a tail. This was seen in light curves
    all across the TESS field of view.

@@

\begin{figure*}[!t]
	%\gridline{
	%  \fig{cluster_field_star_positions.png}{0.49\textwidth}{}
	%  \fig{sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png}{0.49\textwidth}{}
	%}
	\begin{center}
		\leavevmode
		\includegraphics[width=0.97\textwidth]{galacticcoords_cluster_field_star_positions.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Positions of light curves from TESS Sectors 6
			and 7 in galactic coordinates.}
        Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm Rp}<16$
        target stars.  The target stars are mostly near the galactic
        plane.
		\label{fig:lcgalactic}
	}
\end{figure*}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{quilt_PCs.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf Phased light curves for six of the \numberpcs candidate
    transiting planets identified in this work.}
    Black points are detrended flux measurements, phased to the
    best-fit orbital period indicated in the lower right of each
    panel.
    Best-fit models are fit as described in \S~\ref{subsec:ctois}, and
    plotted with blue lines.
    For display purpses, a window of $\pm 4$ transit durations
    centered on the transit mid-point is displayed.
    The vetting reports for these objects are available at XXX.	%FIXME
    % TODO: include age? T mag?
    The Gaia source identifiers are
    a): 5605128927705695232, 
    b): 3125263468681400320, 
    c): 5510676828723793920, 
    d): 3007171311355035136, 
    e): 5617126180115568256, 
    f): 3220266049321724416.   
	\label{fig:ctoi_quilt}
	}
\end{figure*}
